The paper on \Large \bf Blockchain Frontrunning

### 2018-08-30 frontrunning/Latex/sections/paper.tex
[frontrunning] CASE STUDY
[frontrunning] notes from meeting Aug 30

\section{Introduction}
% Why is this important.
% PAPER BEING SOLD HERE
%______________________________________________________________%

@@

@@

\subsection{Literature on Tranditional Front-running}
As traditional frontrunning has been the subject of discussion for decades, there are many literatures on this subject. Here we focus on the historical context and how the regulations evolved to be what they are today.\\
Front-running was first appeared on the Chicago Board Options Exchange ( \textit{CBoE}) ~\cite{markham1988front}, and was identified by \textit{Securities Exchange Commission} in 1977 as the following:
\begin{quote}
The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{Block in the stock market is large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades. ~\cite{sec1978optionsmarket}
\end{quote}

@@

\subsection{Historical evidence in the Blockchain}
As blockchain records are immutably recorded, there is enough historical data to analyze for possible front running detection. For examples here we research some of the events of such attacks happening in the Ethereum blockchain applications.

@@

\subsubsection{Status ICO} \hfill\\ 
\noindent As discussed in ~\ref{sec:Front Running on the Blockchains}, capped ICOs are a good application for front-running attacks.  In June 2017, Status.im~\cite{statuswhitepaper} started their ICO and within 3 hours they reached their cap, resulted in close to 300,000 Ether of funding. They used a \textit{fair} token distribution method called \textit{Dynamic ceiling}, which was in place to prevent large investments to take place early and limited the amount of Ether deposited, this was an attempt to increase the time window for smaller investors. They implemented multiple caps --ceiling-- which each would have a maximum amount that can be deposited. In this case every deposit would be checked by the smart contract and the exceeding amount would be refunded to the sender while the accepted amount would be sent to the Status.im wallet ~\cite{statusicoanalysis}. 
On the time of the ICO there were reports of Ethereum network being unusable and transactions were not confirming. Further study showed that some mining pools might have been manipulating the network for their own profit.

@@

@@

@@

%What is Bancor and how it can be front-run:%
\subsubsection{Bancor} \hfill\\
\noindent Bancor is an Ethereum-based application that allows users to exchange their tokens without any counter-party risk. This protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}-- ERC20 compatible tokens with a built-in liquidity mechanism that are always available to users. Smart Tokens can be bought and sold through the users smart contract at an automatically calculated price which displays supply and demand. Doing so, Bancor protocol provides continuous liquidity for digital assets without relying on an order book as there is no requirement to match sellers and buyers.

@@

%NOTE: @mahsa: is this considered a Historical evidence? should we talk about this somewhere else and maybe do a PoC on Ghazal for this section?
\subsubsection{Domain Name Front-running} \hfill\\    %Following section talks about front-running in namespaces but limited to Ghazal. Will talk about NameCoin in the section of mitigations (commit & reveal method)
\noindent As mentioned in Section~\ref{sec:Front Running on the Blockchains}, although front-running attacks have been more showcased in the context of decentralized exchanges and trading systems, they are are not yet limited to the financial markets. Front-running can occur within other (non-financial) blockchain applications such as naming systems. Blockchain-based domain registrar have been introduced to eliminate the role of central parties \ie domain name system (DNS) which introduce single point of failures in the entire web. One such system is Ghazal, an Ethereum-based naming and PKI system~\cite{moosavighazal}. Ghazal users rely on the Ethereum blockchain to register their \texttt{.ghazal} domain names and bind certificates to those names. In Ghazal model, a user would register domain name by executing the \textit{registerdomain} function from the Ghazal smart contract with the domain name in plain text as the function argument. As mentioned before, These transactions will sit in the mempool so that it would be mined by Ethereum miners and included in the block. During this period in which the transaction is not yet confirmed, front-running attack can occur by (i) dishonest miners and/or (ii) regular non-miner user. In the first case, a miner would intercept the \textit{registerdomain} transaction and register that name ahead of the user. A regular non-miner node in the Ethereum network can front-run other user's \textit{registerdomain} at a good profit by paying higher transaction fees. This practice allows the adversarial party  to register an unregistered domain immediately after someone searched for it, and sell the domain name to the users for a higher price. Note that, domain name front-running also occurs in the vanilla system. In this case, front-runners would monitor and identify domain names of interest, and sell it back to the other users with a higher price~\cite{sac022en33:online}.
% PoC of front-running ghazal
%TODO: also talk about ENS

@@

\subsubsection{Design Decision \#2:Privacy Preserving Blockchian\newline}

@@

@@

\noindent\emph{Eliminating Price Dynamics:} In the context of decentralized exchanges where orderly and fair execution of the orders (transactions) cannot be guaranteed,  another solution is to replace the order book with the \emph{limit order book}. In such design, orders are not executed automatically and an auction process helps the users to choose the orders they want to execute against. By doing so, even if the orders are front-run by other users or miners, there would be no price improvement and financial benefits as the orders are limited.

>>>>

\section{Introduction}

\textbf{CASE STUDY} should be used in here, also in abstract, also at the end of intro section

% Why is this important.
% PAPER BEING SOLD HERE
%______________________________________________________________%

%TODO: Censorship vs frontrunning ! can withholding a transaction be considered as frontrunning? 
%using frontrunning losely, we do not want to defining what exactly front running is, but talking about possibiities of attacks in this nature and also how to prevent these from happening .

@@

%TODO:  do this on top 10 Dapps, based on gas usage or a website. we wanted to look through the popular dapps but there's no such a list . therefor we used different examples as we could came up with. 
%maybe look into cryptokitties breed() if it is possible to front run any section
%possible : maybe top 25 active daily usage DApps from dappradar.com

@@

\subsection{Literature on Traditional Front-running}
As traditional frontrunning has been the subject of discussion for decades, there are many literatures on this subject. Here we focus on the historical context and how the regulations evolved to be what they are today.\\
Front-running was first appeared on the Chicago Board Options Exchange ( \textit{CBoE}) ~\cite{markham1988front}, and was identified by \textit{Securities Exchange Commission} in 1977 as the following:
\begin{quote}
The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{Block in the stock market is large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades. ~\cite{sec1978optionsmarket}
\end{quote}

@@

\section{Historical evidence in the Blockchain}
As blockchain records are immutably recorded, there is enough historical data to analyze for possible front running detection. For examples here we research some of the events of such attacks happening in the Ethereum blockchain applications.

%TODO: talk about why these three. just for emprical /theorical examples, there are tons of examples of front-running, here's three that we chose that are way different. one is emprical that we had to build tools to

@@

\subsection{Status ICO} \hfill\\ 
\noindent As discussed in ~\ref{sec:Front Running on the Blockchains}, capped ICOs are a good application for front-running attacks.  In June 2017, Status.im~\cite{statuswhitepaper} started their ICO and within 3 hours they reached their cap, resulted in close to 300,000 Ether of funding. They used a \textit{fair} token distribution method called \textit{Dynamic ceiling}, which was in place to prevent large investments to take place early and limited the amount of Ether deposited, this was an attempt to increase the time window for smaller investors. They implemented multiple caps --ceiling-- which each would have a maximum amount that can be deposited. In this case every deposit would be checked by the smart contract and the exceeding amount would be refunded to the sender while the accepted amount would be sent to the Status.im wallet ~\cite{statusicoanalysis}. 
On the time of the ICO there were reports of Ethereum network being unusable and transactions were not confirming. Further study showed that some mining pools might have been manipulating the network for their own profit.

@@

%TODO: talk about the tools made to figure this out , it's ok to use jargons and technical terms. maybe a paragraph or two on this, with interfaces and service. ethereum-etl, google bigquery, ...

@@

%TODO: this might not considered as the definition of frontrunning, but it is common to use frontrunning for this so we do the same.

@@

%What is Bancor and how it can be front-run:%
\subsection{Bancor} \hfill\\
\noindent Bancor is an Ethereum-based application that allows users to exchange their tokens without any counter-party risk. This protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}-- ERC20 compatible tokens with a built-in liquidity mechanism that are always available to users. Smart Tokens can be bought and sold through the users smart contract at an automatically calculated price which displays supply and demand. Doing so, Bancor protocol provides continuous liquidity for digital assets without relying on an order book as there is no requirement to match sellers and buyers.

@@

%NOTE: @mahsa: is this considered a Historical evidence? should we talk about this somewhere else and maybe do a PoC on Ghazal for this section?
\subsection{Domain Name Front-running} \hfill\\    %Following section talks about front-running in namespaces but limited to Ghazal. Will talk about NameCoin in the section of mitigations (commit & reveal method)
\noindent As mentioned in Section~\ref{sec:Front Running on the Blockchains}, although front-running attacks have been more showcased in the context of decentralized exchanges and trading systems, they are are not yet limited to the financial markets. Front-running can occur within other (non-financial) blockchain applications such as naming systems. Blockchain-based domain registrar have been introduced to eliminate the role of central parties \ie domain name system (DNS) which introduce single point of failures in the entire web. One such system is Ghazal, an Ethereum-based naming and PKI system~\cite{moosavighazal}. Ghazal users rely on the Ethereum blockchain to register their \texttt{.ghazal} domain names and bind certificates to those names. In Ghazal model, a user would register domain name by executing the \textit{registerdomain} function from the Ghazal smart contract with the domain name in plain text as the function argument. As mentioned before, These transactions will sit in the mempool so that it would be mined by Ethereum miners and included in the block. During this period in which the transaction is not yet confirmed, front-running attack can occur by (i) dishonest miners and/or (ii) regular non-miner user. In the first case, a miner would intercept the \textit{registerdomain} transaction and register that name ahead of the user. A regular non-miner node in the Ethereum network can front-run other user's \textit{registerdomain} at a good profit by paying higher transaction fees. This practice allows the adversarial party  to register an unregistered domain immediately after someone searched for it, and sell the domain name to the users for a higher price. Note that, domain name front-running also occurs in the vanilla system. In this case, front-runners would monitor and identify domain names of interest, and sell it back to the other users with a higher price~\cite{sac022en33:online}.
% PoC of front-running ghazal
%TODO: also talk about ENS

%TODO: ian goberg: private information retrieval . talk about domain name frontrunning in the traditional sense and how goDaddy can steal the domain when queried for availablity. however in blockchain the queiry is private and does not reveal the intention that you want to buy the domain. View only / solidity code on how to enable this

@@

\subsubsection{Design Decision \#2:Privacy Preserving Blockchain\newline}

@@

% TODO: also talk about drawbacks, more expensinve, more transactions, UX, forget to reveal.

@@

%TODO: maybe remove this 
%\noindent\emph{Eliminating Price Dynamics:} In the context of decentralized exchanges where orderly and fair execution of the orders (transactions) cannot be guaranteed,  another solution is to replace the order book with the \emph{limit order book}. In such design, orders are not executed automatically and an auction process helps the users to choose the orders they want to execute against. By doing so, even if the orders are front-run by other users or miners, there would be no price improvement and financial benefits as the orders are limited.
